Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Describe repository level analysis and add a threat to internal validity

\begin{equation}
  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
\end{equation}

@@

\TODO{Level 3: Boxplots}

>>>>

\begin{equation}
  \label{eq:weightedAverage}
  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
\end{equation}

@@

\subsubsection{Repository-level}
The analysis on this level is very similar to the analyis on the author-level. It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to reiceive an average for the whole repository. But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be infered from the results.

Instead, on this level we opted to create boxplots with the rates for each criterion for all authors. Since each author has one triple per ciriterion, this means that for example a repository with 100 authors has 100 datapoints (rates) for a boxplot. The boxplots will be shown and discussed in \ref{sec:results}.

### 2015-08-26 presentations/paper/threats.tex
Describe repository level analysis and add a threat to internal validity

>>>>

Generating boxplots on the author-level assumes equal significance for each author. This means, that an author with just 20 commits and a success-rate of 100\% for a criterion is counted equally as an author with 1000 commits and a rate of 100\%, although always adhering to a guideline for 1000 commits is a way greater feat as doing the same for 20 commits. Maybe this should somehow be reflected in the results, but we estimate that the changes to the result would be insignificant, as long as we exclude authors with very few commits (which we do).
